Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
trim use of em/en dashes
I've never really liked these, as they take the flow out of sentences,
even more than parentheses. They also aren't necessary when commas suffice.

In \sklearn, model selection is supported in two distinct meta-estimators,
\texttt{GridSearchCV} and \texttt{RandomizedSearchCV}.  They take as inputs an
estimator (basic or composite), whose hyper-parameters must be optimized, and a
hyper-parameter grid, which defines the values to search. Optionally, they can
also take a cross-validation scheme and a score function.  The library provides
various such cross-validation schemes, including K-Fold (default), Leave-One-Out
and Bootstrap. The score function used by default is the \texttt{score} method
provided by the estimator. However, the library provides a variety of
score functions that the user can choose instead, including -- among many others
-- accuracy, AUC, $F_1$-score for classification; $R^2$ score or mean squared
error for regression and the Rand Index for clustering.

@@

Our rule of thumb is that user code should not be tied to \sklearn -- which is a
\textit{library}, and not a \textit{framework}. This principle indeed avoids a
well-known problem with object-oriented design, which is that users wanting a
``banana'' should not get ``a gorilla holding the banana and the entire jungle''
(J.~Armstrong, cited by \citealp[p.~213]{seibel2009coders}).  That is, programs
using \sklearn should be easily reusable with other machine learning toolkits or
in other contexts, because they don't need to be intimately tied to it.

@@

The authors and contributors acknowledge active support from INRIA. Past and
present sponsors of the project also include Google -- for funding code
scholarships (\textit{Google Summer of Code}) --, the Python Software Fundation and
Tinyclues -- for funding coding sprints.

>>>>

In \sklearn, model selection is supported in two distinct meta-estimators,
\texttt{GridSearchCV} and \texttt{RandomizedSearchCV}.  They take as inputs an
estimator (basic or composite), whose hyper-parameters must be optimized, and a
hyper-parameter grid, which defines the values to search. Optionally, they can
also take a cross-validation scheme and a score function.  The library provides
various such cross-validation schemes, including K-Fold (default), Leave-One-Out
and Bootstrap. The score function used by default is the \texttt{score} method
provided by the estimator. However, the library provides a large variety of
score functions that the user can choose instead,
including accuracy, AUC, $F_1$-score for classification;
$R^2$ score or mean squared error for regression
and the Rand index for clustering.

@@

Our rule of thumb is that user code should not be tied to \sklearn---which is a
\textit{library}, and not a \textit{framework}. This principle indeed avoids a
well-known problem with object-oriented design, which is that users wanting a
``banana'' should not get ``a gorilla holding the banana and the entire jungle''
(J.~Armstrong, cited by \citealp[p.~213]{seibel2009coders}).  That is, programs
using \sklearn should be easily reusable with other machine learning toolkits or
in other contexts, because they don't need to be intimately tied to it.

@@

The authors and contributors acknowledge active support from INRIA. Past and
present sponsors of the project also include Google for funding code
scholarships (\textit{Google Summer of Code}),
the Python Software Fundation and Tinyclues for funding coding sprints.
